### 2017-04-04 sec-model.tex
Update paper to incorporate reviewer C's comments.
Also update our response to reviewer C to include more concrete
information about what we have changed in the paper and where to find
these changes.

Given a MOOC log, we can define a set $\mathbf{A}$ of actions that a
student can take at any given time. For example, an action $a \in
\mathbf{A}$ might be ``viewing lecture'', ``taking quiz'', or ``viewing
forum''. For each student in the course $\ell \in \mathbf{L}$, we then
extract a list of action sequences $\mathbf{S}_\ell$ that he or she
produced as observed in the log, where each sequence $\mathbf{s} \in
\mathbf{S}_\ell$ is itself a list of actions $(a_1, a_2, \ldots, a_M)$ with
each $a_i \in \mathbf{A}$.  Each sequence can be divided flexibly; in this
paper we chose to denote the end of a sequence as occurring when no further
actions occur within a 10 hour window of time (and thus our sequences
roughly correspond to one day's worth of activity).

>>>>

Given a MOOC log, we can define a set $\mathbf{A}$ of actions that a
student can take at any given time. For example, an action $a \in
\mathbf{A}$ might be ``viewing lecture'', ``taking quiz'', or ``viewing
forum''. For each student in the course $\ell \in \mathbf{L}$, we then
extract a list of action sequences $\mathbf{S}_\ell$ that he or she
produced as observed in the log, where each sequence $\mathbf{s} \in
\mathbf{S}_\ell$ is itself a list of actions $(a_1, a_2, \ldots, a_M)$ with
each $a_i \in \mathbf{A}$.  Each sequence can be divided flexibly; in this
paper we chose to denote the end of a sequence as occurring when no further
actions occur within a 10 hour window of time (and thus our sequences
roughly correspond to one day's worth of activity). This decision reflects
our desire to uncover latent state transition behavior at the granularity
of day-to-day behavior. A different segmentation strategy could be used to
uncover hour-by-hour behavior, or week-by-week behavior, and this depends
entirely on the desired time resolution one wishes to be exhibited in the
transitions between the latent states. Different segmentation strategies
will result in different underlying training data, and this different
meanings behind the patterns that the 2L-HMM will extract.
